\documentclass[10pt,a4paper]{article}

% PACKAGES
\usepackage[utf8]{inputenc}
\usepackage[top=0.4in, bottom=0.3in, left=0.4in, right=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{charter}

% COLOR DEFINITIONS
\definecolor{primarycolor}{RGB}{34, 34, 85}
\definecolor{secondarycolor}{RGB}{50, 110, 160}
\definecolor{rulecolor}{RGB}{160, 170, 190}

% HYPERLINK SETUP
\hypersetup{colorlinks=true, linkcolor=secondarycolor, urlcolor=secondarycolor, citecolor=secondarycolor}

% PAGE STYLE
\pagestyle{empty}
\setlength{\parindent}{0pt}

% SECTION FORMATTING
\titleformat{\section}
  {\normalsize\bfseries\color{primarycolor}}
  {}
  {0em}
  {}[\vspace{1pt}{\color{rulecolor}\titlerule[0.6pt]}]
\titlespacing{\section}{0pt}{6pt}{3pt}

% LIST SPACING
\setlist[itemize]{leftmargin=13pt, itemsep=1pt, topsep=2pt, parsep=0pt, partopsep=0pt}

\begin{document}

% -------------------- HEADER --------------------
\begin{center}
    {\LARGE\bfseries\color{primarycolor} Abdelrahman Abouroumia}
    \vspace{3pt}

    \small
    \faEnvelope\ \href{mailto:aabouroumia@gmail.com}{aabouroumia@gmail.com} \quad
    \faPhone\ +20 110 047 1572 \\[2pt]
    \faLinkedin\ \href{https://linkedin.com/in/abdelrahman-abouroumia}{linkedin.com/in/abdelrahman-abouroumia} \quad
    \faGithub\ \href{https://github.com/Ab-Romia}{github.com/Ab-Romia} \quad
    \faCode\ \href{https://huggingface.co/Ab-Romia}{huggingface.co/Ab-Romia} \\[3pt]
    {\normalsize \faGlobe\ \href{https://romia.dev}{\textbf{\color{secondarycolor}romia.dev}} \ $\cdot$ \ \textit{Portfolio with case studies, architecture breakdowns, and interactive demos}}
\end{center}

% -------------------- SUMMARY --------------------
\section{Summary}
Software engineer with production experience across the full stack: multi-agent AI systems, FastAPI and Spring Boot backends, event-driven microservices with Kafka, and React/Next.js frontends. Co-founded Zaylon AI and shipped a multi-tenant commerce platform integrating 6 e-commerce platforms with tri-lingual NLP serving real users.

% -------------------- EXPERIENCE --------------------
\section{Experience}

\textbf{Software Engineer \& Co-Founder} \hfill \textbf{May 2025 -- Present} \\
\textit{\href{https://zaylon.ai}{Zaylon AI}}
\begin{itemize}
\item Built full-stack platform: \textbf{Next.js}/React merchant dashboard, \textbf{FastAPI} Python backend, \textbf{Docker} containerized deploy.
\item Designed multi-agent \textbf{LangGraph} orchestration routing conversations to 3 specialized agents with 10 scoped AI tools.
\item Integrated \textbf{6 e-commerce platforms} via \textbf{REST APIs} with webhook-driven sync, idempotent operations, and retry logic.
\item Engineered \textbf{DialectBridge}: tri-lingual NLP with auto dialect detection for English, Egyptian Arabic, and Franco-Arabic.
\item Developed hybrid search (keyword + semantic + \textbf{RRF}) and visual product matching via \textbf{GPT-4o} across 3 channels.
\item Built \textbf{PostgreSQL}/\textbf{Redis} data layer with multi-tenant isolation, row-level security, and RFM segmentation analytics.
\end{itemize}

\vspace{4pt}
\textbf{Software Integration Engineering Intern} \hfill \textbf{Jul 2025} \\
\textit{Ejada}
\begin{itemize}
\item Built \textbf{Spring Boot} RESTful APIs for core banking integration with query optimization and \textbf{Redis} caching.
\item Configured \textbf{Apache Kafka} producers and consumers for async event-driven messaging and service decoupling.
\item Implemented API gateway security (OAuth2, rate limiting, request validation) using \textbf{WSO2 API Manager}.
\end{itemize}

\vspace{4pt}
\textbf{AI Coding Expert} \hfill \textbf{Sep 2024 -- Feb 2026} \\
\textit{Freelance}
\begin{itemize}
\item Reviewed and ranked thousands of Python code samples for \textbf{RLHF pipelines}; built quality rubrics for frontier AI models.
\item Developed prompting strategies and evaluation criteria measuring correctness, efficiency, and edge case handling.
\end{itemize}

\vspace{4pt}
\textbf{Automotive Cybersecurity Intern} \hfill \textbf{Aug 2024 -- Oct 2024} \\
\textit{Swift-ACT}
\begin{itemize}
\item Built security scenario catalogs with threat models and mitigations for \textbf{CAN bus} and \textbf{ECU} communication systems.
\item Ran attack simulations (spoofing, replay, DoS) in \textbf{Dyna4} and \textbf{CARLA} against in-vehicle network architectures.
\item Used \textbf{Vector CANoe} for CAN simulation, fault injection, and ECU validation; fuzz-tested \textbf{AEB} braking components.
\end{itemize}

% -------------------- SELECTED PROJECTS --------------------
\section{Selected Projects \hfill \normalfont\small\color{secondarycolor}\faGlobe\ \href{https://romia.dev}{\textbf{Case studies and live demos at romia.dev}}}

\textbf{AI-Powered Collaborative Workspace} \hfill \textit{Graduation Project, Ongoing}
\begin{itemize}
\item Building a \textbf{FastAPI} microservices backend with a context-aware AI assistant for organizational collaboration.
\item Implementing multi-source \textbf{RAG pipeline} with \textbf{PostgreSQL/pgvector} hybrid search and automated document processing.
\end{itemize}

\vspace{3pt}
\textbf{Virtual Banking Microservices} \hfill \href{https://github.com/Ab-Romia/Virtual-Bank-System}{\faGithub\ GitHub}
\begin{itemize}
\item Architected event-driven microservices with \textbf{Spring Boot} and \textbf{Kafka} for banking operations with OAuth2 security.
\item Integrated a \textbf{LangChain}-powered AI agent as an independently scalable microservice for conversational banking.
\end{itemize}

\vspace{3pt}
\textbf{ContextIQ: Production RAG System} \hfill \href{https://huggingface.co/spaces/Ab-Romia/Context-Aware-AI}{\faCode\ Demo} \ \ \href{https://github.com/Ab-Romia/ContextIQ-RAG}{\faGithub\ GitHub} \\
\textbf{FastAPI} RAG API supporting 11+ file formats with hybrid retrieval (TF-IDF + vector) and \textbf{ChromaDB} vector search.

\vspace{3pt}
\textbf{Multimodal Emotion Recognition} \hfill \href{https://huggingface.co/spaces/Ab-Romia/RAVDESS-emotion-recognition}{\faCode\ Demo} \ \ \href{https://github.com/Ab-Romia/RAVDESS-emotion-recognition}{\faGithub\ GitHub} \\
Cross-modal attention model fusing \textbf{HuBERT} audio and \textbf{EfficientNet} visual encoders with bidirectional fusion (8 classes).

\vspace{3pt}
\textbf{Other:}
\href{https://huggingface.co/spaces/Ab-Romia/voiceprint-humanizer}{VoicePrint} (Sentence-BERT style transfer) $\cdot$
\href{https://huggingface.co/spaces/Ab-Romia/connect4-ai}{Connect4 AI} (minimax, alpha-beta) $\cdot$
\href{https://huggingface.co/spaces/Ab-Romia/sudoku-ai}{CSP Sudoku Solver} (AC-3, MRV)

% -------------------- EDUCATION --------------------
\section{Education}
\textbf{Alexandria University, Faculty of Engineering} \hfill \textbf{Expected Jul 2026} \\
B.Sc. in Computer \& Communications Engineering (AI Concentration) \quad $\cdot$ \quad Cumulative GPA: \textbf{3.73 / 4.0} \\
\textit{Coursework:} Data Structures, OOP, Software Engineering, Networks, Databases, OS, Computer Vision, Deep Learning

% -------------------- TECHNICAL SKILLS --------------------
\section{Technical Skills}
\begin{tabular}{@{}p{0.12\textwidth}p{0.87\textwidth}@{}}
\textbf{Languages} & Python, Java, JavaScript/TypeScript, SQL, C/C++ \\
\textbf{Backend} & Spring Boot, FastAPI, Microservices, Kafka, REST APIs, OOP, Design Patterns, Webhooks, PostgreSQL, Redis \\
\textbf{Frontend} & React, Next.js, HTML5, CSS3, Tailwind CSS, Responsive Design \\
\textbf{AI / ML} & LangGraph, LangChain, PyTorch, RAG, Vector DBs (ChromaDB, pgvector), Computer Vision, NLP \\
\textbf{DevOps} & Docker, Git, GitHub Actions, CI/CD, Google Cloud, AWS, Linux, Bash \\
\end{tabular}

% -------------------- BOTTOM --------------------
\vspace{2pt}
\noindent\textbf{Certifications:} \href{https://www.kaggle.com/certification/badges/abdelrahmanromia/105}{Google AI Agents Capstone} (Kaggle) \ $\cdot$ \ Meta Back-end Developer (Coursera) \ $\cdot$ \ AWS Cloud \& ML Foundations \\[1pt]
\textbf{Competitions:} MTC-AIC3 BCI (Egypt National AI) \ $\cdot$ \ ECPC (3x) \ $\cdot$ \ Hepsiburada NLP Hackathon (TEKNOFEST) \\[1pt]
\textbf{Languages:} English (Fluent) $\cdot$ Arabic (Native) $\cdot$ German (A2) $\cdot$ Spanish (Conversational)

\end{document}
